Augmenting the DonorsChoose.org Corpus for Meta-Learning

### 2019-05-06 doc/paper/main.tex
paper/main.tex: Add LMU as affiliation and strip

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, ancollin@tcd.ie, aizawa@nii.ac.jp}
}

@@

\section{Introduction}
Meta-Learning is the process of applying machine learning algorithms on metadata of previous machine learning experiments. The goal is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}. In recommender systems it is an emerging field of interest as meta-learning promises to utilize patterns in metadata as to retrieve the best possible match of item and user. In order to investigate meta-learning algorithms, the required metadata needs to be computed in advance.

>>>>

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	}
\author{Gordian~Edenhofer\inst{1,3} \and Andrew~Collins\inst{2} \and Akiko~Aizawa\inst{3} \and Joeran~Beel\inst{2,3}\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Ludwig Maximilian University of Munich, Faculty of Physics, Germany\\ \and
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{g.edenhofer@campus.lmu.de, ancollin@tcd.ie, aizawa@nii.ac.jp, beelj@tcd.ie}
}

@@

\section{Introduction}
Meta-Learning is the process of applying machine learning algorithms on metadata of previous machine learning experiments. The goal is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}. In recommender systems it is an emerging field of interest as it utilizes patterns in metadata. In order to investigate meta-learning, the required metadata needs to be computed in advance.
